---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$ regchg = \beta_0 + \beta_1 x_{t,i} + \beta_2 x_{p,i} + \beta_3 x_{t,i}*x_{p,i} + \epsilon_i$$

* Describe the population for which you are creating the model.

The population is Kenyan voters in several communities who were either in the control group or were in the treatment group (treatment = presence of local administrator at their polling place).

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

The treatmentLocal:poverty_n coefficient represents the interaction between the slopes of those in local treatment and those of different poverty levels (normalized) 
```{r}
fitted_obj <- stan_glm(data = week_9, reg_chg ~ treatment*poverty_n, refresh = 0)

print(fitted_obj, detail = FALSE, digits = 5)
```

## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?
Wisdom would suggest we exercise caution in determining if the dataset can be used. While we do have info on polling station/data on the local treatment condition — so we could use posterior_predict.

* Describe the ideal Preceptor Table.
We would have no missing values, including all omitted and confounding variables. For polling station 007/001, both under treatment and control, during January of the year.

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r}
new_obs <- tibble(poll_station = c("007/001"),
                  poverty_n = -1.60835093,
                  treatment = c("local"))


pp <- posterior_predict(fitted_obj, 
                        newdata = new_obs) %>%
  as_tibble() %>% 
  mutate_all(as.numeric)

#use backticks for spaces or when it starts with a number
pp %>% 
  rename(station = `1`) %>% 
  ggplot(aes(station)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   fill = "lightgoldenrod", 
                   bins = 125,
                   color = "white") +
    labs(title = "Posterior Predictive Distribution",
         subtitle = "Polling Station 007/001, Under Local Treatment in January",
         x = "Change in Registration",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()

```

* Answer the President's question.

About 1.5% probability


## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 

```{r}
new_obs <- tibble(poverty_n = 2,
                  treatment = c("local"))

pe <- posterior_epred(fitted_obj, 
                      newdata = new_obs) %>%
  as_tibble() 

pe %>% 
  rename(poorcomm = `1`) %>% 
  ggplot(aes(poorcomm)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   fill = "bisque3", 
                   bins = 150,
                   color = "white") +
    labs(title = "Posterior Predictive Distribution",
         subtitle = "Polling Station 007/001, Under Local Treatment in January",
         x = "Change in Registration",
         y = "Probability") + 
    scale_x_continuous(labels = scales::number_format()) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic()


```

